\chapter{Introduction}

\pagestyle{useheadings} % enable header and footer for other pages
\pagenumbering{arabic}


% What's the problem to be solved?
This work gives a general introduction to chatbots
by explaining what they are, what they can be used for and how to develop them.
\\
No previous domain-specific knowledge is required.
\\

% Why is it a problem?
Lately as of writing topics around chatbots have received increasing attention from media and also numerous investments from different actors in the industry.
\\
At the same time not many potential users know about the existence of chatbots or about areas in which chatbots could be helpful assistance.
The topic is equally unknown to developers.
\\
While the term \emph{chatbot} is commonly used in media, the meaning mostly remains ambiguous.
\\
There is a need for further explanation of what chatbots are and further analysis to identify well suited applications for chatbots.
\\
Additionally to spreading knowledge about the potentials of chatbots and their use cases,
more developers should be enabled to create new, innovative chatbots.
\\

% How do I intent to solve it?
The lack of knowledge can be solved by providing answers to the questions of what chatbots are, what benefits they bring and how to create them.
\\
An appropriate definition of chatbots can be given by analyzing the fundamental meaning of the term \emph{chatbot} and by exploring past and current applications.
\\
Use cases of chatbots can be identified by exploring existing applications. Additionally, market trends and attributes of media and technologies can be analyzed to find new potential scenarios for the usage of chatbots.
\\
Development is best explained by creating a real chatbot and by using it to present the general principles of the development process.
\\

% How will this help the world?
Explaining what chatbots are, demystifying what to use them for and presenting how to create them,
will help more people to be able to use and create chatbots, and thereby, accelerate the development of the chatbot ecosystem.
\\
Innovation in technology and the creation of new solutions can help automating and simplifying more tasks,
which gives people the opportunity to focus on more interesting issues and accomplish more things.
\\
Chatbots have the potential to simplify and automate many existing tasks and thereby accelerate the overall technological progress.
\\

% How is this work structured?
The structure of this work follows the three main questions.
\\
To begin with, terminology is defined and applications are explored to form a definition and understanding of what chatbots are.
\\
Afterwards use cases of chatbots are identified not only through the collection of existing examples, but also through the exploration of future potentials by analyzing attributes of the relevant technologies.
\\
The second half of the work is a case study for the development of a chatbot.
The presented example guides through the process of designing user interactions for a chatbot, and additionally explains architectural decisions and technological choices, which provide a basis for other developers to build on when creating new chatbots in the future.
