\section{Present Day}
\label{presentday}


With more than sixty years of history the concept of chatbots is not a recent discovery.
\\
People have been fascinated with the idea of being able to \emph{talk to computers} for a long time;
but past attempts have mostly been simple experiments or applications focused on the aspect of entertainment associated with machines inspired by \emph{science fiction}.
\\

Lately the technology industry and press are increasingly interested in the topic of conversational interfaces and chatbots.
\\
The reinforced interest can be explained by observing recent developments of technology and current market trends.
\\

Since Apple's release of \emph{Siri}~\cite{iphonelaunch} in 2011 customers have become more aware of the possibilities of conversational interfaces.
Even though the capabilities were limited at that time,
functionality improved quickly in the following years,
which can be attributed to the new competition Apple triggered in the market.
\\

At the same time artificial intelligence gained new traction due to the success of using \emph{artificial neural networks} for machine learning.
\\

The concept of artificial neural networks ``dates back to the 1950s, and many of the key algorithmic breakthroughs occurred in the 1980s and 1990s''~\cite{airevolution},
but only now they are successfully applied.
\\
This is mainly due to the increased computing power available today.
A second crucial condition is the necessity for a large disposable amount of data;
big Internet companies specialize on collecting data, originally intended to better target advertisement,
but now they can use their data to train artificial neural networks.
\\
The technology is named \emph{artificial neural network} because they are modeled after neural networks in the human brain;
instead of specifying rules of what a program should do, the machine learns from examples in similar ways to how humans learn.
Some tasks that are too complex to be solved with a rule-based program, can now be solved by collecting enough example data,
letting the machine figure out the solution instead.
\\
These techniques can also be applied in the field of natural language processing,
which is essential to understanding and generating text for conversational interfaces.
\\

With new technical possibilities more people see \emph{conversation as an interface} not only as an idea of science fiction movies,
but instead as something that could be possible in the real world.
\\

Also recent market trends make chatbots more compelling.
\\
``Computing is rapidly shifting to mobile devices''~\cite{mobileusage} and ``messaging apps have surpassed social networks in monthly active users''~\cite{convtrends}.
As a result of these developments users do not have space for complex interfaces on the small screens of their devices,
they need solutions light-weight in data consumption, and they can not use complicated keyboard shortcuts.
At the same time, users are already spending a majority of their time in instant messaging applications
and therefore, they are well accustomed to chatting as means of communication.
\\

Originating from the current state of technology the increasing interest in conversational interfaces leads to new platforms, products and applications for chatbots.
