\section{Communication}
\label{communication}

Nowadays there are two fundamental ways a chatbot can communicate with users;
some platforms provide user interface elements, such as buttons, that can be used;
otherwise communication is done solely with natural language.
\\

Interface elements limit user input to a number of predefined actions,
while natural language has no restrictions on possible inputs.
\\
By suggesting possible actions in the form of a list of buttons or something similar,
possible interactions become obvious and simpler for the user.
\\
Even when limiting interaction to predefined actions,
the main characteristics of a chatbot remain;
the interaction is still structure in the form of a conversation.
\\

In certain scenarios there are too many possible user inputs to fit them in a list.
In these cases natural language is a more appropriate input method.
\\
Custom input requires to be parsed to extract information.
As an example, when the user is asked for a date and time but the situation also allows for repeated times,
a user could express that as \emph{"every second Tuesday at 6am and 9pm"},
while in a traditional user interface this would require a non-trivial amount of interface elements.
\\

If natural language is used for communication,
it should be clearly stated what kind of input is expected
since the user is not able to know which topics and variations of input a system understands.
\\
One of the main challenges with a natural language interface is handling the non-restricted interacted
in a coherent way;
since user input is in no way limited to a single topic,
all sorts of unexpected user reactions have to be accounted for.
\\
As a consequence of this, there are certain conversations every chatbot has to be able to handle in some way.
This includes, but is not limited to, simple smalltalk such as questions like \emph{"How are you today?"}.
\\

Most platforms allow for a combination of the discussed communication mechanisms;
predefined actions can be displayed as suggestions to the user,
while the user is still able to use natural language.
\\
By combining both methods it can be taken advantage of the benefits of both;
there is a clear guideline for interactions and, simultaneously,
the user is free to express any possible custom input.
