\section{Existing Solutions}
\label{existing}


When starting a new projects it is helpful to research for existing solutions that might solve the same problem.
\\

There is already a variety of existing software applications for language studying, which have very different use cases and solve different problems.
\\

One significant separation is between software that includes content and software users can customize to study personal content.
\\

The first segment is the most prominent.
This software is intended to enable people to self-study language and, at least partially, replace physical language courses.
\\
A main reason for the prominence of this segment can be attributed to the ability to sell content.
Professionally curating the curriculum for a language course requires teaching expertise and is a lot of effort. Because of this content remains expensive, not only in software but also in the form of physical textbooks.
\\
One popular example from this segment is \emph{Duolingo}. ``Duolingo has courses in a handful of languages.... The courses are structured in a way like games as well - you earn skill points as you complete lessons''~\cite{lifehacker}.
\\
Interestingly, \emph{Duolingo} recently released a chatbot~\cite{topbots2} as part of their \emph{iPhone} application which enables the user to have a written conversation about certain topics with a chatbot to learn the appropriate phrases for the given scenario.
Although the topics and possible phrases are restricted in each scenario, this is a first example of how chatbots can be used for language studying.
\\

The second segment consists of software which does not provide users a guideline what to study but instead is intended to support users studying their own content.
\\
Most of the software that can be found in this segment are attempts to bring traditional flashcards to digital media.
\\

One of the most established applications in this segment is \emph{Anki}~\cite{lifehacker}, which exists for more than ten years already and provides a flexible, but also rather complex, interface to create a various kinds of studying material.
\\
Another more recent competitor is \emph{Memrise}, where users get a more intuitive interface, which also includes several gamification\footnote{The Oxford Dictionaries describe gamification as ``the application of typical elements of game playing (e.g. point scoring, competition with others, rules of play) to other areas of activity''~\cite{oxfordgamification}} features to make the studying process more appealing.
\\

Both mentioned products are not restricted to a field of study and users are able to add their own content.
Furthermore both products also offer mechanisms for users to share content with others, which allows users to reuse what other users created.
\\

For the here planned chatbot example the second segment is more fitting, since there are no resources in the current context to curate professional content.
\\
The following implementation is an attempt at creating a software product with a conversational text interface that is in its use cases similar to products like \emph{Anki} and \emph{Duolingo} while making use of the unique features the medium chatbot provides.
